% Document class and font size
\documentclass[a4paper,9pt]{extarticle}

% Packages
\usepackage[utf8]{inputenc} % For input encoding
\usepackage{geometry} % For page margins
\geometry{letterpaper, margin=0.75in} % Set paper size and margins
\usepackage{titlesec} % For section title formatting
\usepackage{enumitem} % For itemized list formatting
\usepackage{hyperref} % For hyperlinks
\usepackage{tabularx}
\usepackage{fancyhdr}

% Formatting
\setlist{noitemsep} % Removes item separation
\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}[\titlerule] % Section title format
\titlespacing*{\section}{0pt}{\baselineskip}{\baselineskip} % Section title spacing
\pagestyle{fancy} % Enable headers
\renewcommand{\headrulewidth}{0pt} % Remove header rule
\fancyhead{} % Clear header
\fancyhead[L]{\textit{John Doe}}
\fancyhead[R]{\textit{\# month \#year}}
\thispagestyle{empty} % Remove header from the first page

% Begin document
\begin{document}

% Header
\begin{flushleft}
    \textbf{\LARGE Aarush Sinha}\\[2pt] % Name
    Chennai, India \\
    \href{mailto:aarush.sinha@gmail.com}{aarush.sinha@gmail.com} | \href{https://www.linkedin.com/in/asj10/}{LinkedIn} | \href{https://github.com/chungimungi}{GitHub} % Contact info
\end{flushleft}

% Education Section
\section*{RESEARCH INTERESTS}
\noindent
Natural Language Processing, Information Retrieval, QA-Systems

% Education Section
\section*{EDUCATION}
\noindent
\textbf{Vellore Institute of Technology}, Chennai, India \hfill Sep 2021 | Jun 2025\\ % University name and location
Bachelor of Technology in Computer Science and Engineering \hfill Cumulative GPA: 3.26/4.00 \\
\begin{itemize}
    \item Member of IEEE Computer Science Society.
    \item Member of IEEE RAS.
    \item Part of the college newsletter editorial team.
    \item Part of the university design team.
\end{itemize}

\noindent
\textbf{Kendriya Vidyala, IIT Madras}, Chennai, India \hfill Aug 2016 | May 2021\\ % University name and location
Schooling \hfill Final Grade: 93.8 % Degree and GPA

% Academic Experience Section
\section*{ACADEMIC EXPERIENCE}
\noindent
\textbf{Indian Institute of Technology Madras} \hfill Chennai, India\\ % Company name and location
\textit{Research Intern} \hfill Aug 2023 | Present % Position and duration

Working on implementing generative pseudo labelling for the retrieval of scientific literature by synthetically generating queries. This research is being done under Prof. Nirav Bhatt.

\noindent
\textbf{Olam} \hfill Chennai, India\\ % Company name and location
\textit{Intern} \hfill Jun 2022 | Oct 2022 % Position and duration

Worked with the security team of the company to build a web app for generating weekly user reports.

% Projects Section
\section*{PROJECTS}
\noindent
\textbf{Generation-of-Colors-using-BiLSTMs} \href{https://github.com/chungimungi/Generation-of-Colors-using-BiLSTMs}{GitHub}

A prompt-based model trained to generate colors.

\noindent
\textbf{Predicting-Diseases} \href{https://github.com/chungimungi/Predicting_Diseases}{GitHub}

A custom cross encoder used to predict diseases based on the input of symptoms a user describes in natural language.

\noindent
\textbf{BiGATOR} \href{https://github.com/chungimungi/BiGATOR}{GitHub}

An Attention-seeking Gated BiEncoder evaluated and trained on the Lambada dataset.

% Publications Section
\section*{PUBLICATIONS}
\noindent
\textbf{Arxiv}\\
Sinha, A. "Generation Of Colors using Bidirectional Long Short Term Memory Networks." \newline arXiv, 11 Nov. 2023, doi:10.48550/arXiv.2311.06542.

% Courses Section
\section*{COURSES}
\begin{itemize}
    \item \textbf{Natural Language Processing with Attention Models}
    \href{https://www.coursera.org/account/accomplishments/certificate/V3WGDV276MN3}{Certificate}

    \item \textbf{Natural Language Processing with Classification and Vector Spaces}
    \href{https://www.coursera.org/account/accomplishments/certificate/5TYQZQ95QMC2}{Certificate}

    \item \textbf{Mathematics for Machine Learning: Linear Algebra}
    \href{https://www.coursera.org/account/accomplishments/certificate/KPHRWM5J3BZP}{Certificate}

    \item \textbf{Natural Language Processing in TensorFlow}
    \href{https://www.coursera.org/account/accomplishments/verify/XQ3U9NY2BUKA}{Certificate}
\end{itemize}

% Skills Section
\section*{SKILLS}
\begin{itemize}
    \item \textbf{Programming:} Python, C, Pytorch, Tensorflow, NLP, Machine Learning, Latex
    \item \textbf{Software:} Windows, Linux
    \item \textbf{Soft Skills:} Research, Teamwork, Time Management, Communication
\end{itemize}

% End document
\end{document}
